Titeln på avhandlingens språk

### 2023-01-21 body/part1/overview/implications-optimization.tex
fix
writing

The main question we aim to ask relates to the consequences of using our model of human timing behaviors versus using a less realistic approximation.
Specifically, we aim to quantify the difference in task completion times when using the realistic compared to a baseline model which does not take into consideration higher order effects on execution times.
Our reference baseline corresponds to a first order approximation to empirical execution time modeling, using an \gls{exGaussian} distribution fitted to \emph{all} the data points from \cref{paper:olguinmunoz2021impact} (without any grouping whatsoever) which is randomly sampled to obtain execution time values.

\begin{figure}
    \centering
    \includegraphics[height=13em]{figs/2023EdgeDroid2/task_durations_diff}
    \caption{Difference in task completion times of the realistic model with respect to the reference baseline.
    Bars indicate \SI{95}{\percent} \glspl{CI}.}\label{fig:taskcompletiontimesdiff}
\end{figure}

In \cref{fig:taskcompletiontimesdiff} we present the results of an initial, simulated, exploration of the difference in task execution times generated by the model with respect to the baseline.
A \num{100}-step task is simulated at five different, constant \glspl{TTF}; baseline total duration was, on average, \SI{834.87}{\second}.

>>>>

\begin{figure}
    \centering
    \includegraphics[height=13em]{Figs/2023EdgeDroid2/task_durations_diff}
    \caption{Difference in task completion times of the realistic model with respect to the reference baseline.
    Bars indicate \SI{95}{\percent} \glspl{CI}.}\label{fig:taskcompletiontimesdiff}
\end{figure}

The main question we aim to ask relates to the consequences of using our model of human timing behaviors versus using a less realistic approximation.
Specifically, we aim to quantify the difference in task completion times when using the realistic model compared to a baseline which does not take into consideration higher order effects on execution times.
In \cref{fig:taskcompletiontimesdiff} we present the results of an initial exploration of this difference, comparing the total task durations of simulated \num{100}-step tasks.
Our reference baseline corresponds here to a first order approximation to empirical execution time modeling, using an \gls{exGaussian} distribution fitted to \emph{all} the data points from \cref{paper:olguinmunoz2021impact} (without any grouping whatsoever) which is randomly sampled to obtain execution time values.

These results show clear and significant differences in task durations between the realistic model and the baseline, with a reduction of up to \SI{11}{\percent} at low \glspl{TTF} for both levels of neuroticism.
At higher \glspl{TTF}, the high neuroticism parameterization also results in task durations more than \SI{11}{\percent} longer than the baseline.
